Verifying Demonstrations

### 2017-08-10 intro.tex
Adds slides for protest def
Rewrites using Alice as subject

The organizers want to count everyone who participated at any time and in any 
of the locations~\cite{2016DemonstrationsInSeoul}.
(Whereas police are only interested in the maximum crowd at any point in time, 
to deploy enough personnel for crowd-control.)
We thus settle for the following definition.

\begin{definition}[A protest]
  A protest is an event identified by its cause.
\end{definition}

>>>>

\begin{frame}<presentation>
  \begin{example}[Seoul 2016]
    \begin{itemize}
      \item Rallies every weekend.
      \item Starting midday, lasting to late night.
      \item Some stayed for several hours, some for only minutes.
    \end{itemize}
  \end{example}

  \begin{example}[US 2017]
    \begin{itemize}
      \item Women's Marches in several locations.
      \item Marched some distance.
      \item One-time occurrence.
    \end{itemize}
  \end{example}
\end{frame}

\begin{frame}<presentation>
  \begin{example}[Venezuela 2017]
    \begin{itemize}
      \item Daily anti-government rallies.
      \item Multiple locations.
      \item Pro-government rallies too.
    \end{itemize}
  \end{example}
\end{frame}

The organizer Alice want to count everyone who participated at any time and in 
any of the locations~\cite{2016DemonstrationsInSeoul}.
(Whereas police are only interested in the maximum crowd at any point in time, 
to deploy enough personnel for crowd-control.)
We thus settle for the following definition.

\begin{frame}<presentation>
  \begin{remark}
    \begin{itemize}
      \item Organizers want to count anyone who participated \dots
      \item \dots at any time
      \item \dots in any location
    \end{itemize}
  \end{remark}
\end{frame}

\begin{frame}
\begin{definition}[A protest]
  A protest is an event identified by its cause.
\end{definition}
\end{frame}
